\documentclass{article}
\setcounter{section}{-1}

\begin{document}

\title{Game Design Document}
\author{Y Squad; Game Development Studios}

\maketitle
\newpage

\section{General Information}
\subsection{Game Name}
B59 Chronicles

\subsection{Game Description}
Some pixelart rpg thing.

\subsection{Genre}
Pixel art RPG.

\section{Story}
In the light of some terrible accident (The drowning of the
chosen ones village or something idk) your hero is forced
into the world and needs to save his village or something
by learning magic and drinking coffee in B59. And also
defend Aber against the invation from some evil prime minister
or something idk.

\section{Characters}
\subsection{Annie the Grand Wizard}
The wisest of the grand wizards.

\subsection{Arch-Mage Thomas of the Univeristy of Aberystwyth}

\subsection{The Chosen One}
Your typical hero or something.

\subsection{Other Characters}
\begin{itemise}
  \item Laura
  \item Leena
  \item Sophie
  \item Preben
  \item Aaron
\end{itemise}

\section{Level and Enviroment Design}
\subsection{B59}
It got a coffee machine. What else would you expect?

\section{Gameplay}
I think you should be able to run around.
Have a inventory system for quest items.
Maybe in-game puzzles.

\section{User Interface}
Do we actually need buttons?
3 Buttons on top of an animated background (New Game, Continue, Quit).

\section{HUD}
Options to:
\begin{itemise}
  \item Change volumes (Music, Sound Effects)
  \item Quit
\end{itemise}

\section{Sound Design and Music}
Some fancy welsh music idk.

\end{document}
